Holomorphic field theories and higher algebra

### 2022-12-22 draft.tex
getting up to date

\begin{cor}
Only when $F = 3N$ do all holomorphic vector fields lift to a symmetry lifts at the quantum level.
There is, however, a symmetry of {\em divergence-free} holomorphic vector fields at the quantum level for any values of $F$ and~$N$.
\end{cor}

@@

\begin{dfn}
Let {\em moduli space of quantum vacua} $M^q_{\rm vac}(F,N)$ mean the global horizontal sections over $\cM_{\rm vac}(F,N)$ of this sheaf. 
It is a factorization algebra on~$\CC^2$.
(Again, one could focus, for simplicity, on the polydiscs algebra.)
\end{dfn}

>>>>

\begin{cor}
{\em Divergence-free} holomorphic vector fields are a symmetry at the quantum level for any values of $F$ and~$N$.
Only when $F = 3N$ do {\em all} holomorphic vector fields lift to a symmetry lifts at the quantum level.
\end{cor}

@@

\begin{dfn}
Let the {\em moduli space of quantum vacua} $M^q_{\rm vac}(F,N)$ mean the global horizontal sections over $\cM_{\rm vac}(F,N)$ of this sheaf. 
It is a factorization algebra on~$\CC^2$.
(Again, one could focus, for simplicity, on the polydiscs algebra.)
\end{dfn}
